---
title: "Deepfaking"
subtitle: "Analyses"
author: "Sean Hughes"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

.libPaths()


# Dependencies & functions

```{r}

# dependencies -----
library(tidyverse)
library(ggthemes)
library(knitr)
library(kableExtra)
library(broom)
library(effsize)
library(BayesFactor)
library(metafor)
library(ez)
library(schoRsch)
library(nnet)
library(epitools)

options(knitr.kable.NA = "/")

# Ensures that the processed data folder exists
dir.create("models")
dir.create("results")

# functions -----
# round p value using apa format
apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.0001, paste("=", round(p, 4)),
                        ifelse(p < 0.0001, "< .0001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

# calculate cohens d and return its output in tidy format - a helper function for analysis_workflow
tidy_cohens_d <- function(data){
  require(effsize)

  fit <- effsize::cohen.d(DV ~ IV, data = data)

  results <- tibble(cohens_d = fit$estimate,
                    cohens_d_ci_lower = fit$conf.int["lower"],
                    cohens_d_ci_upper = fit$conf.int["upper"])

  return(results)
}

# calculate cohens d and return its output in tidy format - a helper function for analysis_workflow
tidy_ttest_bf <- function(data){
  require(BayesFactor)

  fit <- data %>%
    ttestBF(formula = DV ~ IV, data = .)

  results <- data.frame(bf10 = extractBF(fit)$bf)
  return(results)
}


# full analysis workflow
# NB workflow returns mean_reference and mean_comparison, where reference is the first factor level and comparison is the next highest level.
analysis_workflow <- function(data){

  # frequentist t test
  results_t_test <- data %>%
    group_by(experiment, DV_type) %>%
    do(broom::tidy(t.test(DV ~ IV, data = .))) %>%
    ungroup() %>%
    rename(t = statistic,
           df = parameter,
           p = p.value,
           mean_reference = estimate1,
           mean_comaprison = estimate2)

  # cohens d
  results_cohens_d <- data %>%
    group_by(experiment, DV_type) %>%
    do(tidy_cohens_d(data = .)) %>%
    ungroup()

  # BF t test
  results_bf_t_test <- data %>%
    group_by(experiment, DV_type) %>%
    do(tidy_ttest_bf(data = .)) %>%
    ungroup()

  # combine
  results <-
    full_join(results_t_test,
              results_cohens_d,
              by = c("experiment", "DV_type")) %>%
    full_join(results_bf_t_test,
              by = c("experiment", "DV_type")) %>%
    select(experiment, DV_type,
           mean_reference, mean_comaprison,
           t, df, p, cohens_d, cohens_d_ci_lower, cohens_d_ci_upper, bf10) %>%
    mutate(reportable_result = paste0("Positive video M = ", round(mean_reference, 2), ", Negative video M = ", round(mean_comaprison, 2), ", t(", round(df, 2), ") = ", round(t, 2), ", p ", apa_p_value(p), ", d = ", round(cohens_d, 2), ", 95% CI [", round(cohens_d_ci_lower, 2), ", ", round(cohens_d_ci_upper, 2), "], BF10 = ", round(bf10, 1)))

  return(results)
}

OR_to_d <- function(OR){
  log(OR)*(sqrt(3)/pi)
}

```

# Data and exclusions

```{r}

# full data
data_processed <-
      read_csv("C:/Users/Sean/Desktop/git/Deepfaking/Experiment 1/2. Data/processed/data_processed.csv") %>%
  # set factor levels for t test comparisons
  mutate(experiment_condition = fct_relevel(experiment_condition,
                                            "Positive Video",
                                            "Negative Video")) %>%
  # create exclusion variable for IAT data
  mutate(exclude_iat = ifelse(complete_iat_data == "complete" & passed_iat_performance == TRUE,
                          FALSE, TRUE),
         # if exclude variable is missing, then exclude
         exclude_iat = ifelse(is.na(exclude_iat), TRUE, exclude_iat)) %>%
  # create exclusion variable for missing exploratory question data 
  mutate(exclude_exploratory = ifelse(is.na(memory_of_video_content), TRUE,
                                      ifelse(is.na(diagnosticity_question), TRUE,
                                             ifelse(is.na(demand), TRUE, 
                                                    ifelse(is.na(reactance), TRUE, 
                                                           ifelse(is.na(hypothesis_awareness), TRUE,
                                                                  ifelse(is.na(influence_awareness), TRUE, FALSE))))))) %>%
  #create compound exclusion criteria
  mutate(exclude = exclude_iat + exclude_exploratory)
  
  # remove missing data
data_processed_after_exclusions <- data_processed %>%
  filter(exclude == 0) 


```

# Demographics

```{r}

data_processed %>%
  summarise(n = n(),
            age_mean = mean(age, na.rm = TRUE),
            age_sd = sd(age, na.rm = TRUE),
            excluded_n = sum(exclude > 0),
            excluded_percent = (excluded_n / n) *100) %>%
  mutate_if(is.numeric, round, digits = 1) %>%
  kable(align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_processed %>%
  count(experiment, gender) %>%
  spread(gender, n) %>%
  kable(knitr.kable.NA = "/", align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)



write_csv(data_processed_after_exclusions, "results/data_processed_after_exclusions.csv")

```

# Analyses by study

## Was there a basic evaluative learning effect?

### IAT & self_reports

- by DV
- Differences between experimental condition (positive vs. negative video)

```{r}

results_basic_effect_iat_selfreports <- data_processed_after_exclusions %>%
  rename(IV = experiment_condition) %>%
  gather(DV_type, DV, c(self_reported_rating, IAT_D2_score)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_basic_effect_iat_selfreports, "results/results_basic_effect_iat_selfreports.csv")

results_basic_effect_iat_selfreports %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Behavioral intentions

Only "brand A" and "brand B" responses were considered (i.e., not both, neither, i dont know, or non responses). Counts of each response for each study and experiment condition were calculated, which were then used to calculate an odds ratio. P values were computed via fischer's exact test.

NB Haldane-Anscombe correction was applied to studies where at least one cell contained zero/NA counts, in which case 1 was added to all cells.

```{r}

data_reshaped_intentions_acquisition_ir <- data_processed_after_exclusions %>%
  filter(experiment_condition == c("acquisition_only") &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, stimulus_identity_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, stimulus_identity_condition, brand_A, brand_B)

temp_study_1 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 1) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_2 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 2) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_3 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 3) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_4 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 4) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_5 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 5) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_6 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 6) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_7 <- data_reshaped_intentions_acquisition_ir %>%
  filter(experiment == 7) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

results_basic_effect_intentions_ir <-
  bind_rows(
    as.data.frame(temp_study_1$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 1),
    as.data.frame(temp_study_2$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 2),
    as.data.frame(temp_study_3$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 3),
    as.data.frame(temp_study_4$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 4),
    as.data.frame(temp_study_5$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 5),
    as.data.frame(temp_study_6$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 6),
    as.data.frame(temp_study_7$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 7)
  ) %>%
  select(experiment, OR, OR_ci_lower, OR_ci_upper, p) %>%
  mutate(OR = round(OR, 2),
         OR_ci_lower = round(OR_ci_lower, 2),
         OR_ci_upper = round(OR_ci_upper, 2),
         reportable_result = paste0("OR = ", round(OR, 2), ", 95% CI [", round(OR_ci_lower, 2), ", ", round(OR_ci_upper, 2), "], p ", apa_p_value(p)))

write_csv(results_basic_effect_intentions_ir, "results/results_basic_effect_intentions_ir.csv")

results_basic_effect_intentions_ir %>%
  select(experiment, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


## Was the IR moderated by extinction?

### IAT & self_reports

- by DV
- Differences between experiment conditions, after reverse scoring for stimulus identity.

```{r}

results_moderation_by_extinction <- data_processed_after_exclusions %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_extinction") &
           experiment %in% c(1, 2, 3, 4, 7)) %>%
  rename(IV = experiment_condition) %>%
  mutate(IV = fct_relevel(IV, "acquisition_and_extinction", "acquisition_only")) %>%
  gather(DV_type, DV, c(self_reported_OEC_effect_controlling_stimulus_identity,
                        self_reported_IR_effect_controlling_stimulus_identity,
                        IAT_D2_controlling_stimulus_identity)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_moderation_by_extinction, "results/results_moderation_by_extinction.csv")

results_moderation_by_extinction %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Behavioral intentions

```{r}

data_reshaped_intentions_moderation_by_extinction_ir <- data_processed_after_exclusions %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_extinction") &
           experiment %in% c(1, 2, 3, 4, 7) &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, experiment_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, experiment_condition, brand_A, brand_B)

temp_study_1 <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  filter(experiment == 1) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_2 <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  filter(experiment == 2) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_3 <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  filter(experiment == 3) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_4 <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  filter(experiment == 4) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_7 <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  filter(experiment == 7) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

results_moderation_by_extinction_intentions_ir <-
  bind_rows(
    as.data.frame(temp_study_1$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 1),
    as.data.frame(temp_study_2$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 2),
    as.data.frame(temp_study_3$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 3),
    as.data.frame(temp_study_4$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 4),
    as.data.frame(temp_study_7$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 7)
  ) %>%
  select(experiment, OR, OR_ci_lower, OR_ci_upper, p) %>%
  mutate(OR = round(OR, 2),
         OR_ci_lower = round(OR_ci_lower, 2),
         OR_ci_upper = round(OR_ci_upper, 2),
         reportable_result = paste0("OR = ", round(OR, 2), ", 95% CI [", round(OR_ci_lower, 2), ", ", round(OR_ci_upper, 2), "], p ", apa_p_value(p)))

write_csv(results_moderation_by_extinction_intentions_ir, "results/results_moderation_by_extinction_intentions_ir.csv")

results_moderation_by_extinction_intentions_ir %>%
  select(experiment, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Was the IR moderated by counter conditioning?

### IAT & self_reports

- by DV
- Differences between experiment conditions, after reverse scoring for stimulus identity.

```{r}

results_moderation_by_counterconditioning <- data_processed_after_exclusions %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_counterconditioning") &
           experiment %in% c(5, 6, 7)) %>%
  rename(IV = experiment_condition) %>%
  mutate(IV = fct_relevel(IV, "acquisition_and_counterconditioning", "acquisition_only")) %>%
  gather(DV_type, DV, c(self_reported_OEC_effect_controlling_stimulus_identity,
                        self_reported_IR_effect_controlling_stimulus_identity,
                        IAT_D2_controlling_stimulus_identity)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_moderation_by_counterconditioning, "results/results_moderation_by_counterconditioning.csv")

results_moderation_by_counterconditioning %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Behavioral intentions

```{r}

data_reshaped_intentions_moderation_by_counterconditioning_ir <- data_processed_after_exclusions %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_counterconditioning") &
           experiment %in% c(5, 6, 7) &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, experiment_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, experiment_condition, brand_A, brand_B)

temp_study_5 <- data_reshaped_intentions_moderation_by_counterconditioning_ir %>%
  filter(experiment == 5) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_6 <- data_reshaped_intentions_moderation_by_counterconditioning_ir %>%
  filter(experiment == 6) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

temp_study_7 <- data_reshaped_intentions_moderation_by_counterconditioning_ir %>%
  filter(experiment == 7) %>%
  select(brand_A, brand_B) %>%
  as.matrix() %>%
  epitools::epitab(x = .)

results_moderation_by_counterconditioning_intentions_ir <-
  bind_rows(
    as.data.frame(temp_study_5$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 5),
    as.data.frame(temp_study_6$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 6),
    as.data.frame(temp_study_7$tab) %>%
      drop_na() %>%
      select(OR = oddsratio, OR_ci_lower = lower, OR_ci_upper = upper, p = p.value) %>%
      mutate(experiment = 7)
  ) %>%
  select(experiment, OR, OR_ci_lower, OR_ci_upper, p) %>%
  mutate(OR = round(OR, 2),
         OR_ci_lower = round(OR_ci_lower, 2),
         OR_ci_upper = round(OR_ci_upper, 2),
         reportable_result = paste0("OR = ", round(OR, 2), ", 95% CI [", round(OR_ci_lower, 2), ", ", round(OR_ci_upper, 2), "], p ", apa_p_value(p)))

write_csv(results_moderation_by_counterconditioning_intentions_ir,
          "results/results_moderation_by_counterconditioning_intentions_ir.csv")

results_moderation_by_counterconditioning_intentions_ir %>%
  select(experiment, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Study 7 ANOVA

```{r}

data_study_7 <- data_processed_after_exclusions %>%
  filter(experiment == 7) %>%
  select(unique_id,
         self_reported_IR_effect_controlling_stimulus_identity,
         self_reported_OEC_effect_controlling_stimulus_identity,
         IAT_D2_controlling_stimulus_identity,
         experiment_condition) %>%
  drop_na()

# IAT
fit_study_7_iat <- ez::ezANOVA(data     = data_study_7,
                               dv       = IAT_D2_controlling_stimulus_identity,
                               between  = experiment_condition,
                               wid      = unique_id,
                               type     = 3,
                               detailed = TRUE)



# IR
fit_study_7_ir <- ez::ezANOVA(data     = data_study_7,
                              dv       = self_reported_IR_effect_controlling_stimulus_identity,
                              between  = experiment_condition,
                              wid      = unique_id,
                              type     = 3,
                              detailed = TRUE)

# OEC
fit_study_7_oec <- ez::ezANOVA(data     = data_study_7,
                               dv       = self_reported_OEC_effect_controlling_stimulus_identity,
                               between  = experiment_condition,
                               wid      = unique_id,
                               type     = 3,
                               detailed = TRUE)

# combine results
results_study_7 <-
  bind_rows(anova_out(fit_study_7_iat,
                      etasq = "partial",
                      print = FALSE)$`--- FORMATTED RESULTS ------------------------------------` %>%
              mutate(DV = "IAT"),
            anova_out(fit_study_7_ir,
                      etasq = "partial",
                      print = FALSE)$`--- FORMATTED RESULTS ------------------------------------` %>%
              mutate(DV = "IR"),
            anova_out(fit_study_7_oec,
                      etasq = "partial",
                      print = FALSE)$`--- FORMATTED RESULTS ------------------------------------` %>%
              mutate(DV = "OEC")) %>%
  filter(Effect == "experiment_condition") %>%
  select(DV, Text)

results_study_7 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Meta-analyses

## Basic effect

### IAT & self_reports

```{r}

results_for_meta_basic_effect_iat_selfreports <- results_basic_effect_iat_selfreports %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_basic_effect_iat <- results_for_meta_basic_effect_iat_selfreports %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi   = yi,
      sei  = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_iat,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "IR effect (IAT)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# IR
fit_basic_effect_ir <- results_for_meta_basic_effect_iat_selfreports %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_ir,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "IR effect (self-reported evaluations)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# OEC
fit_basic_effect_oec <- results_for_meta_basic_effect_iat_selfreports %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_oec,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "OEC effect (self-reported evaluations)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_iat, "models/fit_basic_effect_iat.rds")
write_rds(fit_basic_effect_ir, "models/fit_basic_effect_ir.rds")
write_rds(fit_basic_effect_oec, "models/fit_basic_effect_oec.rds")

```

### Behavioral intentions

```{r}

results_for_meta_basic_effect_intentions_ir <- data_reshaped_intentions_acquisition_ir %>%
  pivot_wider(names_from = stimulus_identity_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad,
         bi = brand_B_Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad,
         ci = brand_A_Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good,
         di = brand_B_Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good,
         data = .)
  
fit_basic_effect_intentions_ir <- results_for_meta_basic_effect_intentions_ir %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_intentions_ir,
                addcred = TRUE,
                refline = 0,
                xlim = c(-5, 14),
                at = c(-2, 0, 2, 4, 6, 8))
text(-5, 9, "IR effect (behavioral intentions)", pos = 4)
text(12, 9, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_intentions_ir, "models/fit_basic_effect_intentions_ir.rds")

```

### Across DVs

multilevel meta

```{r fig.height=6.5, fig.width=8}

fit_basic_effect_multivariate <- 
  bind_rows(
    results_for_meta_basic_effect_iat_selfreports %>%
      filter(DV_type %in% c("IAT_D2", "self_reported_IR_effect")),
    results_for_meta_basic_effect_intentions_ir %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2" = "IAT",
                                 "self_reported_IR_effect" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(DV_type, experiment) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         #mods    = ~ DV_type,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_basic_effect_multivariate, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-2.5, 6),
       at = c(-1, 0, 1, 2, 3, 4))
text(-2.5, 23, "Basic IR effect", pos = 4)
text(6, 23, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_multivariate, "models/fit_basic_effect_multivariate.rds")

```

## Moderation by extinction

### IAT & self_reports

```{r}

results_for_meta_extinction <- results_moderation_by_extinction %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_moderation_extinction_iat <- results_for_meta_extinction %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_iat,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.75, 2.75),
                at = c(-1.0, -0.5, 0, 0.5, 1.0, 1.5))
text(-1.75, 7, "Moderation of IR by extinction (IAT)", pos = 4)
text(2.75, 7, "d [95% CI]", pos = 2)

# IR
fit_moderation_extinction_ir <- results_for_meta_extinction %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_ir,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.75, 2.75),
                at = c(-1.0, -0.5, 0, 0.5, 1.0, 1.5))
text(-1.75, 7, "Moderation of IR by extinction (self-reported evaluations)", pos = 4)
text(2.75, 7, "d [95% CI]", pos = 2)

# OEC
fit_moderation_extinction_oec <- results_for_meta_extinction %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_oec,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.75, 2.75),
                at = c(-1.0, -0.5, 0, 0.5, 1.0, 1.5))
text(-1.75, 7, "Moderation of OEC by extinction (self-reported evaluations)", pos = 4)
text(2.75, 7, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_extinction_iat, "models/fit_moderation_extinction_iat.rds")
write_rds(fit_moderation_extinction_ir, "models/fit_moderation_extinction_ir.rds")
write_rds(fit_moderation_extinction_oec, "models/fit_moderation_extinction_oec.rds")

```

### Behavioral intentions

```{r}

results_for_meta_moderation_extinction_intentions_ir <- data_reshaped_intentions_moderation_by_extinction_ir %>%
  pivot_wider(names_from = experiment_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_acquisition_only,
         bi = brand_B_acquisition_only,
         ci = brand_A_acquisition_and_extinction,
         di = brand_B_acquisition_and_extinction,
         data = .) 

fit_moderation_extinction_intentions_ir <- results_for_meta_moderation_extinction_intentions_ir %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_intentions_ir,
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.5, 4),
                at = c(-2, -1, 0, 1, 2))
text(-3.5, 7, "Moderation of IR by extinction (behavioral intentions)", pos = 4)
text(4, 7, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_extinction_intentions_ir, "models/fit_moderation_extinction_intentions_ir.rds")

```

### Across DVs

multilevel meta

```{r fig.height=5.5, fig.width=8}

fit_moderation_by_extinction_multivariate <- 
  bind_rows(
    results_for_meta_extinction %>%
      filter(DV_type %in% c("IAT_D2_controlling_stimulus_identity", "self_reported_IR_effect_controlling_stimulus_identity")),
    results_for_meta_moderation_extinction_intentions_ir %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2_controlling_stimulus_identity" = "IAT",
                                 "self_reported_IR_effect_controlling_stimulus_identity" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(experiment, DV_type) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_moderation_by_extinction_multivariate, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-1.75, 2),
       at = c(-1, -0.5, 0, 0.5, 1))
text(-1.75, 17, "Moderation of IR effect by extinction", pos = 4)
text(2, 17, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_by_extinction_multivariate, "models/fit_moderation_by_extinction_multivariate.rds")

```

## Moderation by counter conditioning

### IAT & self_reports

```{r}

results_for_meta_counterconditioning <- results_moderation_by_counterconditioning %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_moderation_counterconditioning_iat <- results_for_meta_counterconditioning %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_iat,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of IR by counterconditioning (IAT)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# IR
fit_moderation_counterconditioning_ir <- results_for_meta_counterconditioning %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_ir,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of IR by counterconditioning (self-reported evaluations)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# OEC
fit_moderation_counterconditioning_oec <- results_for_meta_counterconditioning %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_oec,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of OEC by counterconditioning (self-reported evaluations)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_counterconditioning_iat, "models/fit_moderation_counterconditioning_iat.rds")
write_rds(fit_moderation_counterconditioning_ir, "models/fit_moderation_counterconditioning_ir.rds")
write_rds(fit_moderation_counterconditioning_oec, "models/fit_moderation_counterconditioning_oec.rds")

```

### Behavioral intentions

```{r}

results_for_meta_moderation_counterconditioning_intentions_ir <- data_reshaped_intentions_moderation_by_counterconditioning_ir %>%
  pivot_wider(names_from = experiment_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_acquisition_only,
         bi = brand_B_acquisition_only,
         ci = brand_A_acquisition_and_counterconditioning,
         di = brand_B_acquisition_and_counterconditioning,
         data = .)

fit_moderation_counterconditioning_intentions_ir <- results_for_meta_moderation_counterconditioning_intentions_ir %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_intentions_ir,
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.5, 4),
                at = c(-2, -1, 0, 1, 2))
text(-3.5, 5, "Moderation of IR by counterconditioning (behavioral intentions)", pos = 4)
text(4, 5, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_counterconditioning_intentions_ir, "models/fit_moderation_counterconditioning_intentions_ir.rds")

```

### Across DVs

multilevel meta

```{r fig.height=4.5, fig.width=8}

fit_moderation_by_counterconditioning_multivariate <- 
  bind_rows(
    results_for_meta_counterconditioning %>%
      filter(DV_type %in% c("IAT_D2_controlling_stimulus_identity", "self_reported_IR_effect_controlling_stimulus_identity")),
    results_for_meta_moderation_counterconditioning_intentions_ir %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2_controlling_stimulus_identity" = "IAT",
                                 "self_reported_IR_effect_controlling_stimulus_identity" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(experiment, DV_type) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_moderation_by_counterconditioning_multivariate, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-2.25, 2),
       at = c(-1.5, -1, -0.5, 0, 0.5, 1))
text(-2.25, 11, "Moderation of IR effect by extinction", pos = 4)
text(2, 11, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_by_counterconditioning_multivariate, "models/fit_moderation_by_counterconditioning_multivariate.rds")

```

# Sensitivity meta-analyses

Also excluded participants who failed to meet mastery criteria in training or testing phases. Question is considered only at the level of meta-analyses, as sample sizes likely to be under powered at study level.

## Demographics

```{r}

data_processed_after_exclusions_sensitivity <- data_processed_after_exclusions %>%
  filter(passed_performance_criterion_acquisition_training == TRUE &
           passed_performance_criterion_acquisition_testing == TRUE)

data_processed_after_exclusions %>%
  mutate(training_and_testing_exclusions = ifelse(passed_performance_criterion_acquisition_training == TRUE & 
                                                    passed_performance_criterion_acquisition_testing == TRUE, 
                                                  FALSE, TRUE)) %>%
  group_by(experiment) %>%
  summarize(original_n = n(),
            excluded_n = sum(training_and_testing_exclusions),
            excluded_percent = mean(training_and_testing_exclusions*100)) %>%
  mutate_if(is.numeric, round, digits = 1) %>%
  kable(align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Basic effect

### IAT & self_reports

```{r}

results_basic_effect_iat_selfreports_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition == "acquisition_only") %>%
  rename(IV = stimulus_identity_condition) %>%
  gather(DV_type, DV, c(self_reported_OEC_effect, self_reported_IR_effect, IAT_D2)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

results_for_meta_basic_effect_iat_selfreports_sensitivity <- results_basic_effect_iat_selfreports_sensitivity %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_basic_effect_iat_sensitivity <- results_for_meta_basic_effect_iat_selfreports_sensitivity %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi   = yi,
      sei  = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_iat_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "IR effect (IAT)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# IR
fit_basic_effect_ir_sensitivity <- results_for_meta_basic_effect_iat_selfreports_sensitivity %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_ir_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "IR effect (self-reported evaluations)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# OEC
fit_basic_effect_oec_sensitivity <- results_for_meta_basic_effect_iat_selfreports_sensitivity %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_oec_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-1.5, 4),
                at = c(-0.5, 0, 0.5, 1.0, 1.5, 2.0, 2.5))
text(-1.5, 9, "OEC effect (self-reported evaluations)", pos = 4)
text(4, 9, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_iat_sensitivity, "models/fit_basic_effect_iat_sensitivity.rds")
write_rds(fit_basic_effect_ir_sensitivity,  "models/fit_basic_effect_ir_sensitivity.rds")
write_rds(fit_basic_effect_oec_sensitivity, "models/fit_basic_effect_oec_sensitivity.rds")

```

### Behavioral intentions

```{r}

data_reshaped_intentions_acquisition_ir_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition == c("acquisition_only") &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, stimulus_identity_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, stimulus_identity_condition, brand_A, brand_B)

results_basic_effect_intentions_ir_sensitivity <- data_reshaped_intentions_acquisition_ir_sensitivity %>%
  pivot_wider(names_from = stimulus_identity_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad,
         bi = brand_B_Outcome_1_Target_1_Good_Outcome_2_Target_2_Bad,
         ci = brand_A_Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good,
         di = brand_B_Outcome_1_Target_1_Bad_Outcome_2_Target_2_Good,
         data = .) 

fit_basic_effect_intentions_ir_sensitivity <- results_basic_effect_intentions_ir_sensitivity %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_basic_effect_intentions_ir_sensitivity,
                addcred = TRUE,
                refline = 0,
                xlim = c(-5, 12),
                at = c(-2, 0, 2, 4, 6, 8))
text(-5, 9, "IR effect (behavioral intentions)", pos = 4)
text(12, 9, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_intentions_ir_sensitivity, "models/fit_basic_effect_intentions_ir_sensitivity.rds")

```

### Across DVs

multilevel meta

```{r fig.height=6.5, fig.width=8}

fit_basic_effect_multivariate_sensitivity <- 
  bind_rows(
    results_for_meta_basic_effect_iat_selfreports_sensitivity %>%
      filter(DV_type %in% c("IAT_D2", "self_reported_IR_effect")),
    results_basic_effect_intentions_ir_sensitivity %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2" = "IAT",
                                 "self_reported_IR_effect" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(experiment, DV_type) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_basic_effect_multivariate_sensitivity, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-2.5, 6),
       at = c(-1, 0, 1, 2, 3, 4))
text(-2.5, 23, "Basic IR effect", pos = 4)
text(6, 23, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_basic_effect_multivariate_sensitivity, "models/fit_basic_effect_multivariate_sensitivity.rds")

```

## Moderation by extinction

### IAT & self_reports

```{r}

results_moderation_by_extinction_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_extinction") &
           experiment %in% c(1, 2, 3, 4, 7)) %>%
  rename(IV = experiment_condition) %>%
  mutate(IV = fct_relevel(IV, "acquisition_and_extinction", "acquisition_only")) %>%
  gather(DV_type, DV, c(self_reported_OEC_effect_controlling_stimulus_identity,
                        self_reported_IR_effect_controlling_stimulus_identity,
                        IAT_D2_controlling_stimulus_identity)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

results_for_meta_extinction_sensitivity <- results_moderation_by_extinction_sensitivity %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_moderation_extinction_iat_sensitivity <- results_for_meta_extinction_sensitivity %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_iat_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-2.25, 2.25),
                at = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0))
text(-2.25, 7, "Moderation of IR by extinction (IAT)", pos = 4)
text(2.25, 7, "d [95% CI]", pos = 2)

# IR
fit_moderation_extinction_ir_sensitivity <- results_for_meta_extinction_sensitivity %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_ir_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-2.25, 2.25),
                at = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0))
text(-2.25, 7, "Moderation of IR by extinction (self-reported evaluations)", pos = 4)
text(2.25, 7, "d [95% CI]", pos = 2)

# OEC
fit_moderation_extinction_oec_sensitivity <- results_for_meta_extinction_sensitivity %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_oec_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-2.25, 2.25),
                at = c(-1.5, -1.0, -0.5, 0, 0.5, 1.0))
text(-2.25, 7, "Moderation of OEC by extinction (self-reported evaluations)", pos = 4)
text(2.25, 7, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_extinction_iat_sensitivity, "models/fit_moderation_extinction_iat_sensitivity.rds")
write_rds(fit_moderation_extinction_ir_sensitivity,  "models/fit_moderation_extinction_ir_sensitivity.rds")
write_rds(fit_moderation_extinction_oec_sensitivity, "models/fit_moderation_extinction_oec_sensitivity.rds")

```

### Behavioral intentions

```{r}

data_reshaped_intentions_moderation_by_extinction_ir_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_extinction") &
           experiment %in% c(1, 2, 3, 4, 7) &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, experiment_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, experiment_condition, brand_A, brand_B)

results_moderation_extinction_intentions_ir_sensitivity <- data_reshaped_intentions_moderation_by_extinction_ir_sensitivity %>%
  pivot_wider(names_from = experiment_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_acquisition_only,
         bi = brand_B_acquisition_only,
         ci = brand_A_acquisition_and_extinction,
         di = brand_B_acquisition_and_extinction,
         data = .)

fit_moderation_extinction_intentions_ir_sensitivity <- results_moderation_extinction_intentions_ir_sensitivity %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_extinction_intentions_ir_sensitivity,
                addcred = TRUE,
                refline = 0,
                xlim = c(-5, 12),
                at = c(-2, 0, 2, 4, 6, 8))
text(-5, 7, "Moderation of IR by extinction (behavioral intentions)", pos = 4)
text(12, 7, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_extinction_intentions_ir_sensitivity, "models/fit_moderation_extinction_intentions_ir_sensitivity.rds")

```

### Across DVs

multilevel meta

```{r fig.height=5.5, fig.width=8}

fit_moderation_by_extinction_multivariate_sensitivity <- 
  bind_rows(
    results_for_meta_extinction_sensitivity %>%
      filter(DV_type %in% c("IAT_D2_controlling_stimulus_identity", "self_reported_IR_effect_controlling_stimulus_identity")),
    results_moderation_extinction_intentions_ir_sensitivity %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2_controlling_stimulus_identity" = "IAT",
                                 "self_reported_IR_effect_controlling_stimulus_identity" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(experiment, DV_type) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_moderation_by_extinction_multivariate_sensitivity, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-1.75, 2),
       at = c(-1, -0.5, 0, 0.5, 1))
text(-1.75, 17, "Moderation of IR effect by extinction", pos = 4)
text(2, 17, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_by_extinction_multivariate_sensitivity, "models/fit_moderation_by_extinction_multivariate_sensitivity.rds")

```

## Moderation by counter conditioning

### IAT & self_reports

```{r}

results_moderation_by_counterconditioning_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_counterconditioning") &
           experiment %in% c(5, 6, 7)) %>%
  rename(IV = experiment_condition) %>%
  mutate(IV = fct_relevel(IV, "acquisition_and_counterconditioning", "acquisition_only")) %>%
  gather(DV_type, DV, c(self_reported_OEC_effect_controlling_stimulus_identity,
                        self_reported_IR_effect_controlling_stimulus_identity,
                        IAT_D2_controlling_stimulus_identity)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

results_for_meta_counterconditioning_sensitivity <- results_moderation_by_counterconditioning_sensitivity %>%
  rename(yi = cohens_d) %>%
  mutate(sei = (cohens_d_ci_upper - cohens_d_ci_lower)/(2*1.96)) %>%
  select(experiment, DV_type, yi, sei)

# iat
fit_moderation_counterconditioning_iat_sensitivity <- results_for_meta_counterconditioning_sensitivity %>%
  filter(str_detect(DV_type, "IAT_D2")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_iat_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of IR by counterconditioning (IAT)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# IR
fit_moderation_counterconditioning_ir_sensitivity <- results_for_meta_counterconditioning_sensitivity %>%
  filter(str_detect(DV_type, "_IR_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_ir_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of IR by counterconditioning (self-reported evaluations)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# OEC
fit_moderation_counterconditioning_oec_sensitivity <- results_for_meta_counterconditioning_sensitivity %>%
  filter(str_detect(DV_type, "_OEC_")) %>%
  rma(yi = yi,
      sei = sei,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_oec_sensitivity,
                xlab = "Cohen's d",
                addcred = TRUE,
                refline = 0,
                xlim = c(-3.2, 3.8),
                at = c(-2.0, -1.0, 0, 1.0, 2.0))
text(-3.2, 5, "Moderation of OEC by counterconditioning (self-reported evaluations)", pos = 4)
text(3.8, 5, "d [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_counterconditioning_iat_sensitivity, "models/fit_moderation_counterconditioning_iat_sensitivity.rds")
write_rds(fit_moderation_counterconditioning_ir_sensitivity,  "models/fit_moderation_counterconditioning_ir_sensitivity.rds")
write_rds(fit_moderation_counterconditioning_oec_sensitivity, "models/fit_moderation_counterconditioning_oec_sensitivity.rds")

```

### Behavioral intentions

```{r}

data_reshaped_intentions_moderation_by_counterconditioning_ir_sensitivity <- data_processed_after_exclusions_sensitivity %>%
  filter(experiment_condition %in% c("acquisition_only", "acquisition_and_counterconditioning") &
           experiment %in% c(5, 6, 7) &
           behavioral_intentions_IR %in% c("brand_A", "brand_B")) %>%
  count(experiment, experiment_condition, behavioral_intentions_IR) %>%
  spread(behavioral_intentions_IR, n) %>%
  # Haldane-Anscombe correction
  group_by(experiment) %>%
  mutate(count_zero = as.logical(max(c(is.na(brand_A), is.na(brand_B))))) %>%
  ungroup() %>%
  mutate(brand_A = ifelse(count_zero, brand_A+1, brand_A),
         brand_A = ifelse(is.na(brand_A), 1, brand_A),
         brand_B = ifelse(count_zero, brand_B+1, brand_B),
         brand_B = ifelse(is.na(brand_B), 1, brand_B)) %>%
  select(experiment, experiment_condition, brand_A, brand_B)

results_moderation_extinction_intentions_ir_sensitivity <- data_reshaped_intentions_moderation_by_counterconditioning_ir_sensitivity %>%
  pivot_wider(names_from = experiment_condition,
              values_from = c(brand_A, brand_B)) %>%
  escalc(measure = "OR",
         ai = brand_A_acquisition_only,
         bi = brand_B_acquisition_only,
         ci = brand_A_acquisition_and_counterconditioning,
         di = brand_B_acquisition_and_counterconditioning,
         data = .)
  
fit_moderation_counterconditioning_intentions_ir_sensitivity <- results_moderation_extinction_intentions_ir_sensitivity %>%
  rma(yi   = yi,
      vi   = vi,
      data = .,
      slab = experiment)

metafor::forest(fit_moderation_counterconditioning_intentions_ir_sensitivity,
                addcred = TRUE,
                refline = 0,
                xlim = c(-5, 12),
                at = c(-2, 0, 2, 4, 6, 8))
text(-5, 5, "Moderation of IR by counterconditioning (behavioral intentions)", pos = 4)
text(12, 5, "Log OR [95% CI]", pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_counterconditioning_intentions_ir_sensitivity,
          "models/fit_moderation_counterconditioning_intentions_ir_sensitivity.rds")

```

### Across DVs

multilevel meta

```{r fig.height=4.5, fig.width=8}

fit_moderation_by_counterconditioning_multivariate_sensitivity <- 
  bind_rows(
    results_for_meta_counterconditioning_sensitivity %>%
      filter(DV_type %in% c("IAT_D2_controlling_stimulus_identity", "self_reported_IR_effect_controlling_stimulus_identity")),
    results_moderation_extinction_intentions_ir_sensitivity %>%
      mutate(d_ci_lower = OR_to_d(exp(yi - vi*1.96)),
             d_ci_upper = OR_to_d(exp(yi + vi*1.96)),
             sei = (d_ci_upper - d_ci_lower)/(1.96*2),
             yi = OR_to_d(exp(yi)),
             DV_type = "Intentions") %>%
      select(experiment, DV_type, yi, sei)
  ) %>%
  mutate(DV_type = dplyr::recode(DV_type,
                                 "IAT_D2_controlling_stimulus_identity" = "IAT",
                                 "self_reported_IR_effect_controlling_stimulus_identity" = "Self-report",
                                 "Intentions" = "Intentions")) %>%
  arrange(experiment, DV_type) %>%
  rma.mv(yi      = yi,
         V       = sei^2,
         random  = ~ 1 | experiment,
         data    = .,
         slab    = paste(experiment, DV_type)) 

forest(fit_moderation_by_counterconditioning_multivariate_sensitivity, 
       xlab = substitute(paste("Cohen's ", italic('d'))),
       addcred = TRUE,
       refline = 0,
       xlim = c(-2.25, 2),
       at = c(-1.5, -1, -0.5, 0, 0.5, 1))
text(-2.25, 11, "Moderation of IR effect by counterconditioning", pos = 4)
text(2, 11, substitute(paste(italic('d'), " [95% CI]")), pos = 2)

# save model fits for making pdf plots for publication
write_rds(fit_moderation_by_counterconditioning_multivariate_sensitivity,
          "models/fit_moderation_by_counterconditioning_multivariate_sensitivity.rds")

```

