---
title: "Experiment 5"
subtitle: "Analyses"
author: "Sean Hughes"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE)
```

.libPaths()

# Dependencies & functions

```{r}

# dependencies -----
library(rstatix)
library(datarium)
library(tidyverse)
library(ggthemes)
library(knitr)
library(kableExtra)
library(broom)
library(effsize)
library(BayesFactor)
library(metafor)
library(ez)
library(schoRsch)
library(nnet)
library(epitools)
library(writexl)
library(readxl)

options(knitr.kable.NA = "/")

# Ensures that the processed data folder exists
dir.create("models")
dir.create("results")

# functions -----
# round p value using apa format
apa_p_value <- function(p){
  p_formatted <- ifelse(p >= 0.0001, paste("=", round(p, 4)),
                        ifelse(p < 0.0001, "< .0001", NA))
  p_formatted <- gsub(pattern = "0.", replacement = ".", x = p_formatted, fixed = TRUE)
  p_formatted
}

# calculate cohens d and return its output in tidy format - a helper function for analysis_workflow
tidy_cohens_d <- function(data){
  require(effsize)

  fit <- effsize::cohen.d(DV ~ IV, data = data)

  results <- tibble(cohens_d = fit$estimate,
                    cohens_d_ci_lower = fit$conf.int["lower"],
                    cohens_d_ci_upper = fit$conf.int["upper"])

  return(results)
}

# calculate cohens d and return its output in tidy format - a helper function for analysis_workflow
tidy_ttest_bf <- function(data){
  require(BayesFactor)

  fit <- data %>%
    ttestBF(formula = DV ~ IV, data = .)

  results <- data.frame(bf10 = extractBF(fit)$bf)
  return(results)
}


# full analysis workflow
# NB workflow returns mean_reference and mean_comparison, where reference is the first factor level and comparison is the next highest level.
analysis_workflow <- function(data){

  # frequentist t test
  results_t_test <- data %>%
    group_by(experiment, DV_type) %>%
    do(broom::tidy(t.test(DV ~ IV, data = .))) %>%
    ungroup() %>%
    rename(t = statistic,
           df = parameter,
           p = p.value,
           mean_reference = estimate1,
           mean_comaprison = estimate2)

  # cohens d
  results_cohens_d <- data %>%
    group_by(experiment, DV_type) %>%
    do(tidy_cohens_d(data = .)) %>%
    ungroup()

  # BF t test
  results_bf_t_test <- data %>%
    group_by(experiment, DV_type) %>%
    do(tidy_ttest_bf(data = .)) %>%
    ungroup()

  # combine
  results <-
    full_join(results_t_test,
              results_cohens_d,
              by = c("experiment", "DV_type")) %>%
    full_join(results_bf_t_test,
              by = c("experiment", "DV_type")) %>%
    select(experiment, DV_type,
           mean_reference, mean_comaprison,
           t, df, p, cohens_d, cohens_d_ci_lower, cohens_d_ci_upper, bf10) %>%
    mutate(reportable_result = paste0("M = ", round(mean_reference, 2), ", M = ", round(mean_comaprison, 2), ", t(", round(df, 2), ") = ", round(t, 2), ", p ", apa_p_value(p), ", d = ", round(cohens_d, 2), ", 95% CI [", round(cohens_d_ci_lower, 2), ", ", round(cohens_d_ci_upper, 2), "], BF10 = ", round(bf10, 1)))

  return(results)
}

OR_to_d <- function(OR){
  log(OR)*(sqrt(3)/pi)
}


```

# Data Exclusions

```{r}

# DATA EXCLUSIONS

# full data
data_processed <-
      read_csv("C:/Users/Sean/Desktop/git/DF-Impression-Formation--Video-and-Audio-/Experiment 5/2. Data/processed/data_processed.csv")%>%

# set factor levels for experimental condition (pos vs. neg video) and video type (genuine vs. deepfaked)
  
  mutate(experiment_condition = fct_relevel(experiment_condition,
                                            "positive video",
                                            "negative video")) %>%
  mutate(video_type = fct_relevel(video_type,
                                            "genuine video",
                                            "deepfake video")) %>%
  
# create an exclusion variable for IAT data
  
  mutate(exclude_iat = ifelse(complete_iat_data == "complete" & passed_iat_performance == TRUE,
                          FALSE, TRUE),
         # if exclude variable is missing, then exclude
         exclude_iat = ifelse(is.na(exclude_iat), TRUE, exclude_iat)) %>%
  
# create exclusion variable for missing exploratory question data 
 
   mutate(exclude_exploratory = ifelse(is.na(memory_of_video_content), TRUE,
                                      ifelse(is.na(diagnosticity_question), TRUE,
                                             ifelse(is.na(demand), TRUE, 
                                                    ifelse(is.na(reactance), TRUE, 
                                                           ifelse(is.na(hypothesis_awareness), TRUE,
                                                                  ifelse(is.na(influence_awareness), TRUE,
                                                                         ifelse(is.na(deepfake_video_check), TRUE, FALSE)))))))) %>%
  
#create compound exclusion criteria
  mutate(exclude = exclude_iat + exclude_exploratory)
  
# remove missing data

data_processed_after_exclusions <- data_processed %>%
  filter(exclude == 0) 

# Write file to disk for hand scoring of open ended questions 
write_xlsx(data_processed_after_exclusions, "results/data_processed_after_exclusions.xlsx")

# Import file after hand scoring of open ended questions
data_processed_after_hand_scoring <- read_xlsx("results/Data_Cleaned_Recoded.xlsx") %>%
  select(-...1)

```

# Data Transformations

```{r}

# DATA TRANSFORMATIONS (ordered alphabetically)

# RECODE ANALYTIC THINKING (CRT):  
data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
    mutate(crt_q1_recoded = ifelse(crt_q1 == 4, 1, 0),
         crt_q2_recoded = ifelse(crt_q2 == 10, 1, 0),
         crt_q3_recoded = ifelse(crt_q3 == 39, 1, 0),
         crt_q4_recoded = ifelse(crt_q4 == 2, 1, 0),
         crt_q5_recoded = ifelse(crt_q5 == 8, 1, 0),
         crt_q6_recoded = ifelse(crt_q6 == "Emily" | crt_q6 == "emily", 1 ,0),
         crt_q7_recoded = ifelse(crt_q7 == 27, 1, 0),
         analytic_thinking_crt_score = crt_q1_recoded + crt_q2_recoded + crt_q3_recoded + crt_q4_recoded + crt_q5_recoded + crt_q6_recoded + crt_q7_recoded)

# RECODE BELIEF IN CONSPIRACY THEORIES SCALE: calculate a mean score
data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(belief_in_conspiracy_mean = (q1_bcti + q2_bcti + q3_bcti + q4_bcti + q5_bcti + q6_bcti + q7_bcti + q8_bcti + q9_bcti + q10_bcti + q11_bcti + q12_bcti + q13_bcti + q14_bcti + q15_bcti)/15) 


# RECODE DEMAND: responses on the demand variable assigned a value of 0 (No Demand) or 1 (Demand)

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(demand_recoded = case_when(grepl("No", demand) ~ 0,
                                    grepl("I", demand) ~ 0,
                                    grepl("Demand", demand) ~ 1)) 

# RECODE DIAGNOSTICITY: responses on the diagnostic variable are assigned a value from 0 (Not Diagnostic) to 3 (Strongly Diagnostic)

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(diagnosticity_question_recoded = case_when(grepl("Not", diagnosticity_question) ~ 0,
                                       grepl("Slight", diagnosticity_question) ~ 1,
                                       grepl("Moderate", diagnosticity_question) ~ 2,
                                       grepl("Strong", diagnosticity_question) ~ 3))

# RECODE EDUCATION: responses on the education variable are assigned a number from lowest education level (1; less that high school) to highest education level (7; doctoral or professional degree)


data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(education_recoded = case_when(grepl("Less than high school", education) ~ 1,
                                       grepl("High school", education) ~ 2,
                                       grepl("Some college", education) ~ 3,
                                       grepl("Associate degree", education) ~ 4,
                                       grepl("Bachelor", education) ~ 5,
                                       grepl("Masters", education) ~ 6,
                                       grepl("Doctoral degree", education) ~ 7,
                                       grepl("Professional degree", education) ~ 7))
    
# RECODE EMPLOYMENT: responses on the employment variable are assigned to one of three categories: those who respond ‘Employed for wages (part-time)’, ‘Employed for wages (full time)’, or ‘Self-employed’ will be assigned to one group (‘Currently Employed’); those who respond ‘Out of work and looking for work’, ‘Out of work and not looking for work’, ‘Retired’, or ‘Unable to work’, will be assigned to a second group (‘Not Currently Employed’) while those who responded ‘A homemaker’, ‘A student’, or ‘military’ will be assigned to a  third group (‘Vocational Occupation’). 

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(employment_recoded = case_when(grepl("full time", employment) ~ "Currently Employed",
                                        grepl("part-time", employment) ~ "Currently Employed",
                                        grepl("Self-", employment) ~ "Currently Employed",
                                        grepl("looking", employment) ~ "Not Currently Employed",
                                        grepl("not looking", employment) ~ "Not Currently Employed",
                                        grepl("Retired", employment) ~ "Not Currently Employed",
                                        grepl("Unable to work", employment) ~ "Not Currently Employed",
                                        grepl("Homemaker", employment) ~ "Vocational Occupation",
                                        grepl("Student", employment) ~ "Vocational Occupation",
                                        grepl("Military", employment) ~ "Vocational Occupation",
                                        grepl("responding", employment) ~ "Prefer Not to Say",
                                        TRUE ~ "missing"))

# RECODE EVALUATIONS: Create two variables (self-report recoded and IAT recoded). An analytic aim (see sections below) is to compare genuine and deepfaked videos in terms of their effect sizes. However, in order to do this, we need to control for the valence of the videos themselves (some conditions got positive videos whereas others got negative videos). So the self-reported rating/IAT score * by -1 for those in the negative video condition. This ensures that the negative and positive videos are being compared along the same dimension (strength) rather than valence, and that deepfake and genuine videos can be directly compared to one another

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>% 
  mutate(self_report_recoded = ifelse(experiment_condition == "negative video", self_reported_rating * -1, self_reported_rating),
         IAT_recoded = ifelse(experiment_condition == "negative video", IAT_D2_score * -1, IAT_D2_score))


# RECODE EXPLORATORY QUESTION CHECKS: responses on this variable assigned a value of 0 (Not Aware it was a Deepfake) or 1 (Aware it was a Deepfake)


data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(deepfake_concept_check_recoded_ = case_when(grepl("Yes", deepfake_concept_check_recoded) ~ 1,
                                                      grepl("No", deepfake_concept_check_recoded) ~ 0)) %>%
  mutate(deepfake_video_check_recoded_ = case_when(grepl("Yes", deepfake_video_check_recoded) ~ 1,
                                                      grepl("No", deepfake_video_check_recoded) ~ 0)) %>%
  mutate(recognised_video_manipulation_ = case_when(grepl("Yes", recognised_video_manipulation) ~ 1,
                                                      grepl("No", recognised_video_manipulation) ~ 0)) %>% 
  mutate(influence_awareness_recoded_ = case_when(grepl("Yes", influence_awareness_recoded) ~ 1,
                                                   grepl("No", influence_awareness_recoded) ~ 0)) %>% 
  mutate(hypothesis_awareness_recoded_ = case_when(grepl("Yes", hypothesis_awareness_recoded) ~ 1,
                                                   grepl("No", hypothesis_awareness_recoded) ~ 0))


# RECODE INCOME: responses on the income variable are assigned a value from 1 (lower income: Less than $25,000) to 8 (higher income: $200,000 or more).

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(income_recoded = case_when(grepl("Less", income) ~ "1",
                                       grepl("34", income) ~ "2",
                                       grepl("35", income) ~ "3",
                                       grepl("74", income) ~ "4",
                                       grepl("75", income) ~ "5",
                                       grepl("100", income) ~ "6",
                                       grepl("19", income) ~ "7",
                                       grepl("200", income) ~ "8",
                                       grepl("know", income) ~ "Don't Know",
                                       grepl("Prefer", income) ~ "Prefer Not to Say")) 

# RECODE OVERCLAIMING SCALE: calculate a mean score
data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
   mutate(overclaiming_mean = (ocq_1 + ocq_2 + ocq_3 + ocq_4 + ocq_5 + ocq_6 + ocq_7 + ocq_8 + ocq_9 + ocq_10 + ocq_11 + ocq_12 + ocq_13 + ocq_14 + ocq_15 + ocq_16 + ocq_17 + ocq_18 + ocq_19 + ocq_20 + ocq_21 + ocq_22 + ocq_23 + ocq_24 + ocq_25 + ocq_26 + ocq_27 + ocq_28 + ocq_29 + ocq_30)/30) 


# RECODE POLITICAL IDENTITY: responses on this variable assigned a value from -3 (Strongly Disagree) to 3 (Strongly Agree) with 0 (Neither Agree nor Disagree) as a midpoint 

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(political_identity_recoded = case_when(grepl("Strongly Agree", political_ideology_identity_1) ~ 3,
                                    grepl("Moderately Agree", political_ideology_identity_1) ~ 2,
                                    grepl("Somewhat Agree", political_ideology_identity_1) ~ 1,
                                    grepl("Neither", political_ideology_identity_1) ~ 0,
                                    grepl("Somewhat disagree", political_ideology_identity_1) ~ -1,
                                    grepl("Moderately disagree", political_ideology_identity_1) ~ -2,
                                    grepl("Strongly disagree", political_ideology_identity_1) ~ -3))


# RECODE POLITICAL IDEOLOGY (SOCIAL): responses on this variable assigned a value from 1 (Strongly Liberal) to 5 (Strongly Conservative) 

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
   mutate(political_ideology_social_issues_recoded = case_when(grepl("Strongly Liberal", political_ideology_social_issues) ~ 1,
                                    grepl("Somewhat Liberal", political_ideology_social_issues) ~ 2,
                                    grepl("Moderate", political_ideology_social_issues) ~ 3,
                                    grepl("Somewhat Conservative", political_ideology_social_issues) ~ 4,
                                    grepl("Strongly Conservative", political_ideology_social_issues) ~ 5))


# RECODE POLITICAL IDEOLOGY (ECONOMIC): responses on this variable assigned a value from 1 (Strongly Liberal) to 5 (Strongly Conservative)

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
    mutate(political_ideology_economic_issues_recoded = case_when(grepl("Strongly Liberal", political_ideology_economic_issues) ~ 1,
                                    grepl("Somewhat Liberal", political_ideology_economic_issues) ~ 2,
                                    grepl("Moderate", political_ideology_economic_issues) ~ 3,
                                    grepl("Somewhat Conservative", political_ideology_economic_issues) ~ 4,
                                    grepl("Strongly Conservative", political_ideology_economic_issues) ~ 5))


# RECODE REACTANCE: responses on the reactance variable assigned a value of 0 (No Reactance) or 1 (Reactance)

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(reactance_recoded = case_when(grepl("No", reactance) ~ 0,
                                    grepl("I", reactance) ~ 0,
                                    grepl("React", reactance) ~ 1)) 

# RECODE RATIONAL EXPERIENTAL INVENTORY (REI): calculate a mean score

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
 
# Reverse the coding on items that require it so higher scores always indicate more rational thinking     (i.e., score goes from 1 to 7, 2 to 6, 3 to 5, 5 goes to 3, 6 goes to 2, and 7 goes to 1)
  
  mutate(q1_rei_recoded = case_when((q1_rei == 1) ~ 7,
                                    (q1_rei == 2) ~ 6,
                                    (q1_rei == 3) ~ 5,
                                    (q1_rei == 4) ~ 4,
                                    (q1_rei == 5) ~ 3,
                                    (q1_rei == 6) ~ 2,
                                    (q1_rei == 7) ~ 1)) %>%
  

  mutate(q4_rei_recoded = case_when((q4_rei == 1) ~ 7,
                                    (q4_rei == 2) ~ 6,
                                    (q4_rei == 3) ~ 5,
                                    (q4_rei == 4) ~ 4,
                                    (q4_rei == 5) ~ 3,
                                    (q4_rei == 6) ~ 2,
                                    (q4_rei == 7) ~ 1)) %>%

  mutate(q6_rei_recoded = case_when((q6_rei == 1) ~ 7,
                                    (q6_rei == 2) ~ 6,
                                    (q6_rei == 3) ~ 5,
                                    (q6_rei == 4) ~ 4,
                                    (q6_rei == 5) ~ 3,
                                    (q6_rei == 6) ~ 2,
                                    (q6_rei == 7) ~ 1)) %>% 

  mutate(q7_rei_recoded = case_when((q7_rei == 1) ~ 7,
                                    (q7_rei == 2) ~ 6,
                                    (q7_rei == 3) ~ 5,
                                    (q7_rei == 4) ~ 4,
                                    (q7_rei == 5) ~ 3,
                                    (q7_rei == 6) ~ 2,
                                    (q7_rei == 7) ~ 1)) %>%
  
  mutate(q10_rei_recoded = case_when((q10_rei == 1) ~ 7,
                                    (q10_rei == 2) ~ 6,
                                    (q10_rei == 3) ~ 5,
                                    (q10_rei == 4) ~ 4,
                                    (q10_rei == 5) ~ 3,
                                    (q10_rei == 6) ~ 2,
                                    (q10_rei == 7) ~ 1)) %>%

  mutate(q13_rei_recoded = case_when((q13_rei == 1) ~ 7,
                                    (q13_rei == 2) ~ 6,
                                    (q13_rei == 3) ~ 5,
                                    (q13_rei == 4) ~ 4,
                                    (q13_rei == 5) ~ 3,
                                    (q13_rei == 6) ~ 2,
                                    (q13_rei == 7) ~ 1)) %>%

  mutate(q15_rei_recoded = case_when((q15_rei == 1) ~ 7,
                                    (q15_rei == 2) ~ 6,
                                    (q15_rei == 3) ~ 5,
                                    (q15_rei == 4) ~ 4,
                                    (q15_rei == 5) ~ 3,
                                    (q15_rei == 6) ~ 2,
                                    (q15_rei == 7) ~ 1)) %>%
  
  mutate(q18_rei_recoded = case_when((q18_rei == 1) ~ 7,
                                    (q18_rei == 2) ~ 6,
                                    (q18_rei == 3) ~ 5,
                                    (q18_rei == 4) ~ 4,
                                    (q18_rei == 5) ~ 3,
                                    (q18_rei == 6) ~ 2,
                                    (q18_rei == 7) ~ 1)) %>%

  mutate(q19_rei_recoded = case_when((q19_rei == 1) ~ 7,
                                    (q19_rei == 2) ~ 6,
                                    (q19_rei == 3) ~ 5,
                                    (q19_rei == 4) ~ 4,
                                    (q19_rei == 5) ~ 3,
                                    (q19_rei == 6) ~ 2,
                                    (q19_rei == 7) ~ 1)) %>%

  mutate(q20_rei_recoded = case_when((q20_rei == 1) ~ 7,
                                    (q20_rei == 2) ~ 6,
                                    (q20_rei == 3) ~ 5,
                                    (q20_rei == 4) ~ 4,
                                    (q20_rei == 5) ~ 3,
                                    (q20_rei == 6) ~ 2,
                                    (q20_rei == 7) ~ 1)) %>%
  
# Rational Scale (normal indicates no reversed scoring and reverse indicates reverse scoring)
#Q1. Reverse Q2. Normal Q6.Reverse Q7. Reverse Q10. Reverse Q11. Normal Q13.Reverse Q15. Reverse Q19. Reverse Q20. Reverse

  mutate(rational_scale_rei = ((q1_rei_recoded + q2_rei + q6_rei_recoded + q7_rei_recoded + q10_rei_recoded + q11_rei + q13_rei_recoded + q15_rei_recoded + q19_rei_recoded + q20_rei_recoded))/10,
 
# Experiential Scale
# Q3.Normal Q4.Reverse Q5. Normal Q8. Normal Q9. Normal Q12. Normal Q14. Normal Q16. Normal Q17. Normal Q18. Reverse
                 
         experiential_scale_rei = ((q3_rei + q4_rei_recoded + q5_rei + q8_rei + q9_rei + q12_rei + q14_rei + q16_rei + q17_rei + q18_rei_recoded)/10)) 
                                 
# RECODE RELIGIOUS AFFILITATION: responses on this variable assigned to one of three categories: Religious, Agnostic, Atheist (note: no religion individuals are assigned to the atheist group)

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
   mutate(religious_affiliation_general_recoded = case_when(grepl("Agnostic", religious_affiliation_general) ~ "Agnostic",
                                    grepl("Atheist", religious_affiliation_general) ~ "Atheist",
                                    grepl("Christian", religious_affiliation_general) ~ "Religious",
                                    grepl("Hindu", religious_affiliation_general) ~ "Religious",
                                    grepl("Humanist", religious_affiliation_general) ~ "Religious",
                                    grepl("Jewish", religious_affiliation_general) ~ "Religious",
                                    grepl("Muslim", religious_affiliation_general) ~ "Religious",
                                    grepl("No religion", religious_affiliation_general) ~ "Atheist",
                                    grepl("Other not listed", religious_affiliation_general) ~ "Religious",
                                    grepl("Sikh", religious_affiliation_general) ~ "Religious"))  


# RECODE RELIGIOUS AFFILITATION SCALE: responses on this variable scored from 1 (I strongly disagree) to 5 (I strongly agree). Responses to each item will be summed to create a total score representing ‘Religiosity’, with higher scores indicating higher religiosity.

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(ras_q1_recoded = case_when(grepl("I strongly disagree", ras_q1) ~ 1,
                                    grepl("I disagree", ras_q1) ~ 2,
                                    grepl("I don't know", ras_q1) ~ 3,
                                    grepl("I agree", ras_q1) ~ 4,
                                    grepl("I strongly agree", ras_q1) ~ 5),
         ras_q2_recoded = case_when(grepl("I strongly disagree", ras_q2) ~ 1,
                                    grepl("I disagree", ras_q2) ~ 2,
                                    grepl("I don't know", ras_q2) ~ 3,
                                    grepl("I agree", ras_q2) ~ 4,
                                    grepl("I strongly agree", ras_q2) ~ 5),
         ras_q3_recoded = case_when(grepl("I strongly disagree", ras_q3) ~ 1,
                                    grepl("I disagree", ras_q3) ~ 2,
                                    grepl("I don't know", ras_q3) ~ 3,
                                    grepl("I agree", ras_q3) ~ 4,
                                    grepl("I strongly agree", ras_q3) ~ 5),
         ras_q4_recoded = case_when(grepl("I strongly disagree", ras_q4) ~ 1,
                                    grepl("I disagree", ras_q4) ~ 2,
                                    grepl("I don't know", ras_q4) ~ 3,
                                    grepl("I agree", ras_q4) ~ 4,
                                    grepl("I strongly agree", ras_q4) ~ 5),
         ras_q5_recoded = case_when(grepl("I strongly disagree", ras_q5) ~ 1,
                                    grepl("I disagree", ras_q5) ~ 2,
                                    grepl("I don't know", ras_q5) ~ 3,
                                    grepl("I agree", ras_q5) ~ 4,
                                    grepl("I strongly agree", ras_q5) ~ 5),
         ras_q6_recoded = case_when(grepl("I strongly disagree", ras_q6) ~ 1,
                                    grepl("I disagree", ras_q6) ~ 2,
                                    grepl("I don't know", ras_q6) ~ 3,
                                    grepl("I agree", ras_q6) ~ 4,
                                    grepl("I strongly agree", ras_q6) ~ 5),
         ras_q7_recoded = case_when(grepl("I strongly disagree", ras_q7) ~ 1,
                                    grepl("I disagree", ras_q7) ~ 2,
                                    grepl("I don't know", ras_q7) ~ 3,
                                    grepl("I agree", ras_q7) ~ 4,
                                    grepl("I strongly agree", ras_q7) ~ 5),
         relgious_affliation_score_mean = ((ras_q1_recoded + ras_q2_recoded + ras_q3_recoded + ras_q4_recoded + ras_q5_recoded + ras_q6_recoded + ras_q7_recoded)/7))


# Order Variables in File for Later Analysis

data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
  mutate(demographic_items = "*",
          method_items = "*",
          evaluative_items = "*",
          exploratory_items = "*",
          individual_difference_items = "*") %>%
  select(numeric_id,
         experiment,
         demographic_items,
         age,
         gender,
         gender_self_describe,
         ethnicity,
         ethnicity_self_describe,
         education,
         education_recoded,
         employment,
         employment_recoded,
         location,
         income,
         income_recoded,
         method_items,
         condition,
         experiment_condition,
         video_type,
         task_order,
         IAT_block_order,
         complete_iat_data,
         passed_iat_performance,
         exclude_iat,
         exclude_exploratory,
         exclude,
         evaluative_items,
         pos_neg,
         good_bad,
         like_dislike,
         self_reported_rating,
         self_report_recoded,
         IAT_D2_score,
         IAT_recoded,
         exploratory_items,
         memory_of_video_content,
         diagnosticity_question,
         diagnosticity_question_recoded,
         demand,
         demand_recoded,
         reactance,
         reactance_recoded,
         hypothesis_awareness,
         hypothesis_awareness_recoded_,
         influence_awareness,
         influence_awareness_recoded_,
         recognised_video_manipulation_,
         deepfake_video_check,
         deepfake_video_check_recoded_,
         deepfake_concept_check,
         deepfake_concept_check_recoded_,
         issues_with_study,
         individual_difference_items,
         political_ideology_identity_1,
         political_ideology_social_issues,
         political_ideology_economic_issues,
         religious_affiliation_general,
         political_identity_recoded,
         political_ideology_social_issues_recoded,
         political_ideology_economic_issues_recoded,
         ras_q1,
         ras_q2,
         ras_q3,
         ras_q4,
         ras_q5,
         ras_q6,
         ras_q7,
         ras_q8,
         religious_affiliation_general_recoded,
         ras_q1_recoded,
         ras_q2_recoded,
         ras_q3_recoded,
         ras_q4_recoded,
         ras_q5_recoded,
         ras_q6_recoded,
         ras_q7_recoded,
         relgious_affliation_score_mean,
         q1_bcti,
         q2_bcti,
         q3_bcti,
         q4_bcti,
         q5_bcti,
         q6_bcti,
         q7_bcti,
         q8_bcti,
         q9_bcti,
         q10_bcti,
         q11_bcti,
         q12_bcti,
         q13_bcti,
         q14_bcti,
         q15_bcti,
         belief_in_conspiracy_mean,
         ocq_1,
         ocq_2,
         ocq_3,
         ocq_4,
         ocq_5,
         ocq_6,
         ocq_7,
         ocq_8,
         ocq_9,
         ocq_10,
         ocq_11,
         ocq_12,
         ocq_13,
         ocq_14,
         ocq_15,
         ocq_16,
         ocq_17,
         ocq_18,
         ocq_19,
         ocq_20,
         ocq_21,
         ocq_22,
         ocq_23,
         ocq_24,
         ocq_25,
         ocq_26,
         ocq_27,
         ocq_28,
         ocq_29,
         ocq_30,
         overclaiming_mean,
         q1_rei,
         q1_rei_recoded,
         q2_rei,
         q3_rei,
         q4_rei,
         q4_rei_recoded,
         q5_rei,
         q6_rei,
         q6_rei_recoded,
         q7_rei,
         q7_rei_recoded,
         q8_rei,
         q9_rei,
         q10_rei,
         q10_rei_recoded,
         q11_rei,
         q12_rei,
         q13_rei,
         q13_rei_recoded,
         q14_rei,
         q15_rei,
         q15_rei_recoded,
         q16_rei,
         q17_rei,
         q18_rei,
         q18_rei_recoded,
         q19_rei,
         q19_rei_recoded,
         q20_rei,
         q20_rei_recoded,
         rational_scale_rei,
         experiential_scale_rei,
         crt_q1,
         crt_q2,
         crt_q3,
         crt_q4,
         crt_q5,
         crt_q6,
         crt_q7,
         crt_q8,
         crt_q9,
         crt_q1_recoded,
         crt_q2_recoded,
         crt_q3_recoded,
         crt_q4_recoded,
         crt_q5_recoded,
         crt_q6_recoded,
         crt_q7_recoded,
         analytic_thinking_crt_score)

# Write file to disk for hand scoring of open ended questions 
write_xlsx(data_processed_after_hand_scoring, "results/data_for_analysis.xlsx")

# Write deepfake only condition subset of data
sean <- data_processed_after_hand_scoring %>%
filter(video_type == "deepfake video") %>%
  write_xlsx("results/deepfake_only.xlsx")
```

# Demographics

```{r}

data_processed_after_hand_scoring %>%
  summarise(n = n(),
            age_mean = mean(age, na.rm = TRUE),
            age_sd = sd(age, na.rm = TRUE),
            excluded_n = sum(exclude > 0),
            excluded_percent = (excluded_n / n) *100) %>%
  mutate_if(is.numeric, round, digits = 1) %>%
  kable(align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_processed_after_hand_scoring %>%
  count(experiment, gender) %>%
  spread(gender, n) %>%
  kable(knitr.kable.NA = "/", align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


```

# Analyses

## 1. Did evaluations differ as a function of video content (positive vs. negative statements)?

### IAT & self_reports

- by DV

```{r}

# Reorder the factor levels on the experiment_condition and video_type variables 

#data_processed_after_hand_scoring <- data_processed_after_hand_scoring %>%
#  mutate(experiment_condition = as.factor(experiment_condition)) %>%
#  mutate(experiment_condition = factor(experiment_condition, levels = c("positive_video", "negative_video"))) %>%
#  mutate(video_type = as.factor(video_type)) %>%
#  mutate(video_type = factor(video_type, levels = c("genuine video", "deepfake video")))
  
# Carry out Analysis

results_iat_selfreports_video_content <- data_processed_after_hand_scoring %>%
  rename(IV = experiment_condition) %>%
  gather(DV_type, DV, c(self_reported_rating, IAT_D2_score)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_iat_selfreports_video_content, "results/results_iat_selfreports_video_content.csv")

results_iat_selfreports_video_content %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


ratings_plot <- data_processed_after_hand_scoring %>%
  group_by(experiment_condition) %>%
  dplyr::summarise(mean_rating = mean(self_reported_rating, na.rm = TRUE),
                   se_rating = sd(self_reported_rating)/sqrt(length(self_reported_rating)), na.rm = TRUE) %>%
  ungroup() 

ggplot(ratings_plot, aes(x=experiment_condition, y=mean_rating, group = 1)) + 
    geom_errorbar(aes(ymin=mean_rating-se_rating, ymax=mean_rating+se_rating), width=.1) +
    geom_line() +
    geom_point()+
   theme_classic() +
  ylim(-2, 2)

IAT_plot <- data_processed_after_hand_scoring %>%
  group_by(experiment_condition) %>%
  dplyr::summarise(mean_IAT = mean(IAT_D2_score, na.rm = TRUE),
                   se_IAT = sd(IAT_D2_score)/sqrt(length(IAT_D2_score)), na.rm = TRUE) %>%
  ungroup() 

ggplot(IAT_plot, aes(x=experiment_condition, y=mean_IAT, group = 1)) + 
    geom_errorbar(aes(ymin=mean_IAT-se_IAT, ymax=mean_IAT+se_IAT), width=.1) +
    geom_line() +
    geom_point()+
   theme_classic() +
  ylim(-.5, .5)


```


## 2. Did evaluations differ as a function of video type (genuine vs. deepfaked)?

### IAT & self_reports

- by DV

```{r}

results_iat_selfreports_video_type <- data_processed_after_hand_scoring %>%
  rename(IV = video_type) %>%
  gather(DV_type, DV, c(self_reported_rating, IAT_D2_score)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_iat_selfreports_video_type, "results/results_iat_selfreports_video_type.csv")

results_iat_selfreports_video_type %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


## 3. Does the strength of evaluation depend on video content (e.g., do positive videos give rise to stronger effects than negative videos)?

### IAT & self_reports

- by DV


```{r}

results_iat_selfreports_evaluation_strength <- data_processed_after_hand_scoring %>%
  rename(IV = video_type) %>%
  gather(DV_type, DV, c(self_report_recoded, IAT_recoded)) %>%
  select(experiment, DV_type, DV, IV) %>%
  drop_na() %>%
  analysis_workflow(data = .)

write_csv(results_iat_selfreports_evaluation_strength, "results/results_iat_selfreports_evaluation_strength.csv")

results_iat_selfreports_evaluation_strength %>%
  select(experiment, DV_type, reportable_result) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## 4. Is there an interaction between video content and video type? 

```{r}

# inspect the four experimental conditions 
data_processed_after_hand_scoring %>% sample_n_by(experiment_condition, video_type, size = 1)

# get summary stats for the four experimental conditions

data_processed_after_hand_scoring %>%
  group_by(experiment_condition, video_type) %>%
  get_summary_stats(self_reported_rating, type = "mean_sd")

# Run the two way ANOVA on video type and content

results_video_type_video_content <- data_processed_after_hand_scoring %>% anova_test(self_reported_rating ~ experiment_condition * video_type)

results_video_type_video_content

```


